Supporting Information

### 2018-04-13 SupportingInformation.Rmd
adding chunk for moran effect

<!--Shya to implement the modelling we discussed on 2018 04 12 and make results appear here!-->

>>>>

<!--Shya to implement the modelling we discussed on 2018 04 12 and make results appear here!-->
```{r cause4copula}
source("Cause4copula.R")
set.seed(seed)
#--------------------------------------------------------------------------------
# when noise comes from a clayton cop with spearmancor=0.8
s<-GetNoise(N=10000,fcode=3,corcoef=0.8,method="spearman",ploton=T)
s2<-Simulator_Cause4copula(cons=0.5,p0=c(0,0),noise=s$noise_q,burnin=1000)
#hist(s2[,1],breaks=1000) # it's normal
s2_p<-pnorm(s2)
#hist(s2_p[,1],breaks=1000) # it's uniform
points(s2_p[,1],s2_p[,2],col="red")

# Now compare between two correlations coming from noise_q and s2_p
cor.test(s$noise_q[,1],s$noise_q[,2],method = "spearman")$estimate
cor.test(s2_p[,1],s2_p[,2],method = "spearman")$estimate

cor.test(s$noise_q[,1],s$noise_q[,2],method = "kendall")$estimate
cor.test(s2_p[,1],s2_p[,2],method = "kendall")$estimate

cor.test(s$noise_q[,1],s$noise_q[,2],method = "pearson")$estimate
cor.test(s2_p[,1],s2_p[,2],method = "pearson")$estimate
#-----------------------------------------------------------------------------------------
# when noise comes from a clayton cop with kendallcor=0.8
s<-GetNoise(N=10000,fcode=3,corcoef=0.8,method="kendall",ploton=T)
s2<-Simulator_Cause4copula(cons=0.5,p0=c(0,0),noise=s$noise_q,burnin=1000)
#hist(s2[,1],breaks=1000) # it's normal
s2_p<-pnorm(s2)
#hist(s2_p[,1],breaks=1000) # it's uniform
points(s2_p[,1],s2_p[,2],col="red")

# Now compare between two correlations coming from noise_q and s2_p
cor.test(s$noise_q[,1],s$noise_q[,2],method = "spearman")$estimate
cor.test(s2_p[,1],s2_p[,2],method = "spearman")$estimate

cor.test(s$noise_q[,1],s$noise_q[,2],method = "kendall")$estimate
cor.test(s2_p[,1],s2_p[,2],method = "kendall")$estimate

cor.test(s$noise_q[,1],s$noise_q[,2],method = "pearson")$estimate
cor.test(s2_p[,1],s2_p[,2],method = "pearson")$estimate
#----------------------------------------------------------------------------------
# when noise comes from a gumbel cop with spearmancor=0.8
s<-GetNoise(N=10000,fcode=4,corcoef=0.8,method="spearman",ploton=T)
s2<-Simulator_Cause4copula(cons=0.5,p0=c(0,0),noise=s$noise_q,burnin=1000)
#hist(s2[,1],breaks=1000) # it's normal
s2_p<-pnorm(s2)
#hist(s2_p[,1],breaks=1000) # it's uniform
points(s2_p[,1],s2_p[,2],col="red")

# Now compare between two correlations coming from noise_q and s2_p
cor.test(s$noise_q[,1],s$noise_q[,2],method = "spearman")$estimate
cor.test(s2_p[,1],s2_p[,2],method = "spearman")$estimate

cor.test(s$noise_q[,1],s$noise_q[,2],method = "kendall")$estimate
cor.test(s2_p[,1],s2_p[,2],method = "kendall")$estimate

cor.test(s$noise_q[,1],s$noise_q[,2],method = "pearson")$estimate
cor.test(s2_p[,1],s2_p[,2],method = "pearson")$estimate
#------------------------------------------------------------------------------------
# when noise comes from a gumbel cop with kendallcor=0.8
s<-GetNoise(N=10000,fcode=4,corcoef=0.8,method="kendall",ploton=T)
s2<-Simulator_Cause4copula(cons=0.5,p0=c(0,0),noise=s$noise_q,burnin=1000)
#hist(s2[,1],breaks=1000) # it's normal
s2_p<-pnorm(s2)
#hist(s2_p[,1],breaks=1000) # it's uniform
points(s2_p[,1],s2_p[,2],col="red")

# Now compare between two correlations coming from noise_q and s2_p
cor.test(s$noise_q[,1],s$noise_q[,2],method = "spearman")$estimate
cor.test(s2_p[,1],s2_p[,2],method = "spearman")$estimate

cor.test(s$noise_q[,1],s$noise_q[,2],method = "kendall")$estimate
cor.test(s2_p[,1],s2_p[,2],method = "kendall")$estimate

cor.test(s$noise_q[,1],s$noise_q[,2],method = "pearson")$estimate
cor.test(s2_p[,1],s2_p[,2],method = "pearson")$estimate

```
